Manuscript analyses

### 2024-01-31 cilta_cel/Manuscript analyses.Rmd
Add help code to build the consort + fix bug

### Tables
Patients evaluable at each time point
```{r evaluable}
day7 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(os_from_infusion_months > (7 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day14 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(os_from_infusion_months > (14 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day21 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(os_from_infusion_months > (21 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day30 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(os_from_infusion_months > (30 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day90 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(os_from_infusion_months > 3) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day180 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(os_from_infusion_months > 6) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
tbl_merge(list(day7, day14, day21, day30, day90, day180), 
          tab_spanner = c("day7", "day14", "day21", "day30", "day90", "day180"))
```

@@

## Figure 1. Consort diagram

>>>>

### Tables
Patients evaluable at each time point
```{r evaluable}
day7 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day14 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day21 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day30 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day90 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
day180 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
mon12 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  filter(pfs_event == 0 | pfs_from_infusion_months > 12) %>% 
  select(pt_identifier) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label()
tbl_merge(list(day7, day14, day21, day30, day90, day180, mon12), 
          tab_spanner = c("day7", "day14", "day21", "day30", "day90", "day180", "month12"))
```

@@

## Figure 1. Consort diagram
This will help for creating the figure. It shows the patients who had PD or died with info of the event.
```{r}
fig_dat %>% 
  mutate(pfs_from_infusion_days = 
           interval(
             start = date_of_car_t_infusion, 
             end = pfs_date)/
           duration(n=1, units = "days")) %>% 
  filter(os_event == 1 | pfs_event == 1) %>% 
  mutate(event_at = case_when(
    !is.na(date_of_pd) & pfs_from_infusion_months < 1        ~ "had pd",
    !is.na(date_of_pd) & pfs_from_infusion_months < 3        ~ "had pd",
    !is.na(date_of_pd) & pfs_from_infusion_months < 6        ~ "had pd",
    !is.na(date_of_pd) & pfs_from_infusion_months < 12       ~ "had pd",
    os_event == 1 & pfs_from_infusion_months < 1        ~ "died",
    os_event == 1 & pfs_from_infusion_months < 3        ~ "died",
    os_event == 1 & pfs_from_infusion_months < 6        ~ "died",
    os_event == 1 & pfs_from_infusion_months < 12       ~ "died",
  )) %>% 
  mutate(phrase = paste("Patient", pt_identifier, event_at, "at day", pfs_from_infusion_days)
  ) %>% 
  arrange(pfs_from_infusion_days) %>% 
  select(phrase, `cause of death` = cause_of_death_myeloma_toxicitiy_unrelated,
         `CRS grade` = max_crs_grade_0_5, `delayed neurotoxicity` = delayed_neuro_type)
```
